Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-04 paper.tex
Respond review wrt constraints and tasks (partial).

The way we generate a goal configuration is the following:
\begin{enumerate}
\item Shoot a random configuration in $\mathcal{C}$ with uniform distribution.
\item Call the \textit{constraint solver} (Algorithm~\ref{algo:newton}) on this configuration, with the static
  balance constraints and the goal task.
\item If success, check for collisions.
\end{enumerate}

@@

Fig.~\ref{fig:goal} shows different random configurations enforcing banlance 
constraints and solving a reaching task for an animated character.

>>>>

The way we generate a goal configuration is the following:
\begin{enumerate}
\item Shoot a random configuration in $\mathcal{C}$ with uniform distribution.
\item \textbf{Call the \textit{constraint solver}
  (Algorithm~\ref{algo:newton}) on this configuration, with the
  intersection of the planning and goal manifolds $\mathcal{M} \cap
  \goalmanifold$.}
\item If success, check for collisions.
\end{enumerate}

@@

\textbf{Fig.~\ref{fig:goal} shows resulting random configurations
  enforcing balance ($\mathcal{M}$) and reaching ($\goalmanifold$)
  constraints for the HRP-2 robot.}
